
\documentclass[sigconf, nonacm]{acmart}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\graphicspath{{./images/}} 

\begin{document}

\title{Everyone wants to do the AI work, not the HCI work}

\author{Danny Liu}

\email{danny_liu_5@sfu.ca}
\affiliation{%
  \institution{Simon Fraser University}
  \streetaddress{8888 University Drive}
  \city{Burnaby}
  \state{B.C.}
  \country{Canada}
}

\begin{abstract}
The increasing popularity of large language models (LLMs), such as ChatGPT, is largely due to enhancements in chat interfaces that have become more intuitive and conversational. These models are proving useful across various domains, including education and computer-supported collaborative work (CSCW). To fully leverage these advancements in data and modeling technology, it is crucial to simultaneously advance the human-computer interaction (HCI) aspects. Enhancing HCI is essential for optimizing user experience when interacting with these tools. Additionally, there is a growing demand for open-source solutions in this field, driven by the need for transparency and trust, as open-source projects allow for greater inspection and modification of the code, fostering a better understanding and acceptance among users. This paper will discuss improvements in the user interfaces of open-source LLMs.
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10011738.10011776</concept_id>
<concept_desc>Human-centered computing~Accessibility systems and tools</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Accessibility systems and tools}
\keywords{Large Language Models, User Interface, Human Centered Artificial Intelligence, Human Computer Interaction}

\maketitle

\section{Introduction}
test

\subsection{Visual Abstract}
test

\subsection{Related Work}
test

\subsubsection{A Third-level Heading} 
test

\subsection{Methods}
Test

\subsection{Results}
Test

\subsection{Discussion}
Test

\subsection{Artifacts}
Test

\begin{acks}
Acknowledgements go here. Delete enclosing begin/end markers if there are no acknowledgements.
\end{acks}
\end{document}